---
title: "Homework 6"
author: Diana Sanchez
output: github_document
---

This is my solution to HW6.

``` {r}
library(tidyverse)
library(readxl)
library(patchwork)
library(modelr)
library(mgcv)
```

## Problem 2

### Loading and cleaning dataset

```{r message=FALSE, warning=FALSE}
bw_df =
  read_csv(
    "./data/birthweight.csv") %>%
  drop_na() %>%
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    mrace = as.factor(mrace),
    malform = as.factor(malform),
    mrace = as.factor(mrace))
```

### Modeling process and predictions vs residuals
```{r}
model_1 = lm(bwt ~ smoken + gaweeks + wtgain, data = bw_df)

train = bw_df %>% 
  add_predictions(model_1) %>% 
  add_residuals(model_1) %>% 
  ggplot(aes(x = resid, y = pred)) + 
  geom_point() + ggtitle("Plot of model residuals against fitted values")

train
```

I used hypothesized a model for birthweight based on previous knowledge. The variables that stood out to me included the average number of cigarettes smoked per day during pregnancy (which usually correlates with a lower birthweight), gestional age in weeks (where we would expect a lower weight for a lower age), and mother's weight gain during pregnancy (where we would expect a larger birthweight if the mom gains more weight).

### Comparing models
```{r}
model_2 = lm(bwt ~ blength + gaweeks, data = bw_df)

model_3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex , data = bw_df)

bw_df2 = 
  crossv_mc(bw_df, 4352) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

bw_df3 = 
  bw_df2 %>% 
  mutate(
    model_1 = map(.x = train, ~lm(bwt ~ smoken + gaweeks + wtgain, data = bw_df)),
    model_2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = bw_df)),
    model_3 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex , data = bw_df)
  )) %>% 
  mutate(
    rmse_1 = map2_dbl(.x = model_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(.x = model_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_3 = map2_dbl(.x = model_3, .y = test, ~rmse(model = .x, data = .y))
  )

bw_df3 %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```


From this violin graph, we can see that the best model is model 3, which includes bhead, blength, babysex and all interaction terms.

## Problem 3

```{r message=FALSE, warning=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weath_3 = weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance),
    results2 = map(models, broom::tidy)) %>%
  select(results, results2) %>%
  unnest(results) %>%
  select(r.squared, results2) %>%
  unnest(results2) %>%
  select(r.squared, term, estimate) %>%
  pivot_wider(
  names_from = "term", 
  values_from = "estimate") %>%
    rename(
    beta_0 = `(Intercept)`,
    beta_1 = tmin) %>%
  mutate(
  log = log((beta_0 * beta_1)))


```

### Distribution plots for r̂2 and log(β̂0∗β)
```{r}
weath_graph1 =
  ggplot(data = weath_3, aes(x = r.squared)) + geom_density()

weath_graph2 =
  ggplot(data = weath_3, aes(x = log)) + geom_density()

weath_graph1 + weath_graph2
```
 
These plots are similar in shape in that they have an overall bell-curve shape. 

### 95% confidence interval for r̂2 and log(β̂0∗β̂)
```{r}
r_2 = pull(weath_3, r.squared)
weath_r = quantile(r_2, c(0.025, 0.975))

log_2 = pull(weath_3, log)
weath_log = quantile(log_2, c(0.025, 0.975))

weath_r %>%
  knitr::kable(
  caption = "95% CI for r̂")

weath_log %>%
  knitr::kable(
    caption = "95% CI for  log(β̂0∗β̂)"
  )
```


