---
title: "Homework 2"
author: Diana Sanchez
output: github_document
---

This is my solution to HW1.

``` {r}
library(tidyverse)
library(readxl)
```

## Problem 1

Read the Mr. Trashwheel data set.

```{r}
trashwheel_df=
  read_xlsx(
    "./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx", 
    sheet = "Mr. Trash Wheel", 
    range = cell_cols("A:N")) %>%
  janitor::clean_names() %>%
  drop_na(dumpster) %>%
  mutate(
    sports_balls = round(sports_balls),
    sports_balls = as.integer(sports_balls)
  )
```

Read precipitation data for 2018 and 2017.

```{r}
precip_2018 = 
  read_xlsx(
    "./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "2018 Precipitation",
    skip = 1
  ) %>%
  janitor::clean_names() %>%
  drop_na(month) %>%
  mutate (year = 2018) %>%
  relocate(year)

precip_2017 = 
  read_xlsx(
    "./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "2017 Precipitation",
    skip = 1
  ) %>%
  janitor::clean_names() %>%
  drop_na(month) %>%
  mutate (year = 2017) %>%
  relocate(year)
```

Combine annual precipitation.

```{r}
month_df=
  tibble(
    month = 1:12,
    month_name = month.name
  )

precip_df=
  bind_rows(precip_2018, precip_2017)

left_join(precip_df, month_df, by = "month")
```

Summarize Mr. Trash Wheel data

This dataset contains information from the MR. Trashwheel trash collector in Baltimore. As trash enters the inner harbor, the trashweel collects that trash, and stores it in a dumpstore. The dataset contains information on year, month, and trash collected, including some specific kinds of trash. There are a total of `r nrow(trashwheel_df)` rows in our final document. Additional data sets include month precipitation data. The median number of sports balls found in a dumpster in 2017 was `r trashwheel_df %>% filter(year == 2017) %>% pull(sports_balls) %>% median()` sports balls. The total precipitation in 2018 was `r precip_df %>% filter(year == 2018) %>% pull(total) %>% sum()` inches.


## Problem 2

Read NYC Transit data.

```{r}
transit_df=
  read_csv("./data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv") %>%
  janitor::clean_names() %>%
  select(line, station_name, route1, route2, route3, route4, route5, route6, route7, route8, route9, route10, route11, station_latitude, station_longitude, entry, vending, entrance_type, ada) %>%
  mutate(entry = recode(entry, "YES" = T, "NO" = F))
```

```{r}
stations = distinct(transit_df, line, station_name, ada)
```

The dataset contains transit data for NYC, specifically related to entrances and exits of each subway station. It includes the variables line, station_name, route1, route2, route3, route4, route5, route6, route7, route8, route9, route10, route11, station_latitude, station_longitude, entry, vending, entrance_type, and ada. The dimensions of the data set are `r nrow(transit_df)` rows x `r ncol(transit_df)` columns.

This is not tidy data.

There are `r nrow(stations)` distinct stations. 

```{r}
stations2=
 mutate(filter (stations, ada == "TRUE"))
```

There are `r nrow(stations2)` ada compliant stations.

```{r}
no_vending=
  mutate(filter (transit_df, vending == "NO"))
```

```{r}
allow_entrance= 
  mutate(filter (no_vending, entry == "TRUE"))
```

The proportion of station entrances / exits without vending allow entrance is `r nrow(allow_entrance)/ nrow(no_vending)`.

## Problem 3
Clean pol-month data

```{r}
pols_month = 
  read_csv(
    "./data/pols-month.csv") %>%
  separate(mon, into = c("year", "month", "day")) %>%
  mutate(month= as.integer(month))

month_df=
  tibble(
    month = 01:12,
    month_name = month.name)

pols_month = left_join(pols_month, month_df, by = "month")

polls_month_mutate = pols_month %>%
  mutate(president = ifelse(prez_dem == 1, "dem", "gop"))

polls_month_mutate2 = 
select(polls_month_mutate, - prez_gop, - prez_dem, - month) %>%
relocate (year, month_name)

```

Clean snp data.

```{r}
snp = 
  read_csv(
    "./data/snp.csv") %>%
  separate(date, into = c("month", "day", "year")) %>%
  mutate(month= as.integer(month))

month_df=
  tibble(
    month = 01:12,
    month_name = month.name)

snp2 = 
  left_join(snp, month_df, by = "month") %>%
  select(- month) %>%
  relocate (year, month_name)

```

Clean unemployment data.
```{r}
unemployment = 
  read_csv(
    "./data/unemployment.csv") %>%
  pivot_longer(
    Jan:Dec,
    names_to = "month",
    values_to = "unemploy"
  )

month_df2=
  tibble(
    month = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
    month_name = month.name)

unemploy_tidy = 
  left_join(unemployment, month_df2, by = "month") %>%
  select(- month) %>%
  relocate(Year, month_name) %>%
  janitor::clean_names()



```

