---
title: "Homework 6"
author: Diana Sanchez
output: github_document
---

This is my solution to HW1.

``` {r}
library(tidyverse)
library(readxl)
```

## Problem 2

Read the birthweight data set.

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

Note that although we expect your model to be reasonable, model building itself is not a main idea of the course and we don’t necessarily expect your model to be “optimal”.



```{r}
bw_df =
  read_csv(
    "./data/birthweight.csv") %>%
  drop_na() %>%
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    mrace = as.factor(mrace),
    malform = as.factor(malform),
    mrace = as.factor(mrace))

model_1 = lm(bwt ~ smoken + malform, data = bw_df)

model_2 = lm(bwt ~ blength + gaweeks, data = bw_df)

model_3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex , data = bw_df)
```


## Problem 3

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weath_3 = weather_df %>% 
  modelr::bootstrap(n = 10) %>% 
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance),
    results2 = map(models, broom::tidy)) %>%
  select(results, results2) %>%
  unnest(results, results2) %>%
  select(r.squared, term, estimate) %>%
  pivot_wider(
  names_from = "term", 
  values_from = "estimate") %>%
  rename(
    beta_0 = `(Intercept)`,
    beta_1 = tmin) %>%
  mutate(
  log = ln(beta_0 * beta_1))

```

